---
title: "Aides Drug Users"
author: "Chelsia Zetina"
date: "May 4, 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(dplyr)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avast=filter(avast, Ivdrug=="user")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new preventative AIDS vaccine is being tested in Clinical trials to keep AIDS from occuring. We want to find out out whether or not the vaccine is effective to IV drug users (free vs. user). We want to consider the effectiveness of the vaccine across this group. 


Does the drug have any affect on whether one contracts AIDS or not. 

$H_0:$ The drug has no effect on whether one contracts AIDS or not


$H_A:$ The drug has an effect on whether one contracts AIDS or not

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

#Results general effectiveness
Is the vaccine effective in the general population 

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data=avast, type='percent') 
```
  This bar chart shows that the IV Drug Users group using the vaccine has a greater chance of contracting AIDS rather than the IV Drug Users using the placebo. 


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
genTable = xtabs(~treatment+infected, data=avast)
print(genTable)
rowPerc(genTable)
colPerc(genTable)
```

This table shows IV Drug Users contracting AIDS; 72% used the vaccine and 28% used the placebo.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~treatment + infected, data=avast)
```


The p-value is very small, printed as 0. Therefore we reject the null hypothesis, there is no relationship between taking the vaccine and getting AIDS.


#Results in IV drug use effectiveness
Does drug use make a difference in vaccine effectiveness?

```{r}
fisher.test(genTable)
```

The odds of getting AIDS is 2.72 to 1, if you take the drug.

# Discussion and Conclusion


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The conclusion is the IV Drug User community using the vaccine are more likely to contract AIDS than using the placebo. The P-value=2.998e-06, I reject the null hypothesis, due to the information provided above that shows the ineffectiveness of using the vaccine rather than the placebo. The vaccine is not helping people contract AIDS.




 