---
title: "Aides Drug Users"
author: "Chelsia Zetina"
date: "May 4, 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(dplyr)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avast=filter(avast, Ivdrug=="user")

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new preventative aides vaccine is being tested in Clinical trials to keep AIDS from occuring. We want to find out out whether or not the vaccine is effective to IV drug users (free vs. user). We want to consider the effectiveness of the vaccine across this group. 

Does have any affect on whether one contracts AIDS or not. 

$H_0:$ The drug has no effect on whether one contracts AIDS or not


$H_A:$ The drug has an effect on whether the drug has any protection against contracting AIDS

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

#Results general effectiveness
Is the vaccine effective in the general population 

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data=avast, type='percent') 
```
This bar chart shows that people that are receiving the vaccine are more likely to get aids than people who received the placebo.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
genTable = xtabs(~treatment+infected, data=avast)
print(genTable)
```

This table shows all the participants of the trial that are getting the vaccine and the results of being infected with AIDS.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~treatment + infected, data=avast)
```

#Results in IV drug use effectiveness
Does drug use make a difference in vaccine effectiveness?

```{r}
xtabs(~treatment+infected, data=avast)
```


# Discussion and Conclusion


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

$H_0$ :  The vaccine has no effect in the contacting aids against the whole population of participants.  

$H_A$ :  The Vaccine will absolutely effecting in protecting a person from contracting aids.  




It is hard to clearly look at the results when just looking at the bar graghs and seeing if the vaccine is effective across all users.  When looking at the numerical data it is easier to see what has a correlation and not. Deciding what is important to the study and analyzing if Avastirinol is effective in preventing aids.  When analyzing the effectiveness of the drug we looked at if the people were drug users, the gender, and the sexual orientation of the person receiving the vaccine or placebo.  Putting all of the data together we do not see a direct correlation from a person receiving Avastirinol and the effectiveness. 

  There is little data comparing when a person has aids or not and if they have received the vaccine the P value is less than  %. We look at the P value because it shows the probability of the same study happening again. If the P value is less than % if rejects the Ho , if the P value is more than we have to accept it.  Since the P value is less that it is not acceptable and does not show any correlation.  The P value when comparing IV drug users and receiving the vaccine is also less than %.  However comparing the sex and their sexual orientation to whether or not they have received the vaccine or not the P value was more than %.  When comparing the sex of the person to the treatment was more than %. The P value for comparing the sexual orientation and the treatment was more  than %. Because the P value was not more than % on all the data across the board this vaccine is deemed to be not useful. 