---
title: "Aids Drug Everybody"
author: "Chelsia Zetina"
date: "May 4, 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(dplyr)
avast <-read.csv(file="avastivironal.csv",header=TRUE)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new preventative aides vaccine is being tested in Clinical trials to keep AIDS from occuring.  We want to consider the effectiveness of the vaccine or the placebo in regards to everyone as a whole. 

Does the drug have any affect on whether one contracts AIDS or not. 

$H_0:$ The drug has no effect on whether one contracts AIDS or not


$H_A:$ The drug has an effect on whether one contracts AIDS or not

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

For each hypothesis test the graphical summary will be a bar plot, the numerical summary will be a cross tabulation, and a chi-squared test will be used for the inferential results. 

#Results general effectiveness

Is the vaccine effective in the population of everyone

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data=avast, type='percent') 
```
  
  This bar chart shows that everyone using the placebo has a greater chance of getting AIDS rather than the group using the vaccine. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
genTable = xtabs(~treatment+infected, data=avast)
print(genTable)
rowPerc(genTable)
colPerc(genTable)
```

This table shows everyone contracting AIDS, 25% used the vaccine and 75% used the placebo.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~treatment + infected, data=avast)
```


The p-value is very small, printed as 0. So therefore we reject the null hypothesis that there is no relationship between taking the vaccine and getting AIDS. 

#Results in drug use effectiveness for everyone
Does drug use make a difference in vaccine effectiveness?

```{r}
fisher.test(genTable)
```
The odds of getting AIDS is 0.35 to 1, if taking the vaccine. 


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The conclusion is that everyone using the vaccine is less likely contract AIDS than using the placebo. The P-value=4.23e-08, I reject the null hypothesis, due to the information provided above that shows the effectiveness of using the vaccine rather than the placebo. The vaccine is helping people with not contracting AIDS.
